Transfer Learning in Multimodal Compositional and Relational Reasoning

### 2019-11-15 cvpr_submission/transfer_learning.tex
Change to new taxonomy image.
no message
updated image name
Some minor typo corrections.
Finished reasoning trasnfer
Add distinction between zero-shot learning and finetuning at end of transfer learning section.

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}

@@

Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in visual reasoning.
For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
One setting is the case of static images, where this could be due to having different feature combinations in the source and
target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
large in another.
These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries, 
comparison of objects, or existence of objects with certain features etc.
This entails studying transfer learning between families of tasks which requires extending the above definition.

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in just the feature attributes such as shape, color, and size, or their combinations
	thereof.

	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and there is a single task.
	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
	where $n$ equals the maximum number of objects $n$ in an image, and $m$
	equals  the number of frames in a video. 
	For any visual input $v_S$ coming from $X_S$ with $C(v_S) = (n_S, m_S)$
	and for any visual input $v_T$ coming from $X_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
	$m_T \ge m_S$ with at least one inequality being a strict one. 
	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.

@@

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}

@@

Although~\cref{defn:transfer} is quite general, it does not adequately capture all artifacts present in visual reasoning.
For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
One setting is the case of static images, where this could be due to having different feature combinations in the source and
target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
large in another.
These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries, 
comparison of objects, or existence of objects with certain features etc.
This entails studying transfer learning between families of tasks which requires extending the above definition.

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in the feature attributes such as shape, color, and size, or their combinations
	thereof.

	\item[Temporal Transfer:] This setting is similar to attribute adaptation in that $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and there is a single task.
	The key difference is that we introduce a notion of complexity $C(v) = (n, m)$ for a visual input $v$,
	where $n$ equals the maximum number of objects $n$ in an image, and $m$
	equals  the number of frames in a video. 
	For any visual input $v_S$ coming from $\cX_S$ with $C(v_S) = (n_S, m_S)$
	and for any visual input $v_T$ coming from $\cX_T$ with $C(v_T) = (n_T, m_T)$, we require that $n_T \ge n_S$ and 
	$m_T \ge m_S$ with at least one inequality being a strict one. 
	Thus, we necessarily increase the complexity of the visual input going from the source to the target domain.

@@

If labeled data is available for $\cX_T$, a final distinction we make is between \emph{zero-shot learning} and \emph{finetuning}. Finetuning entails the use of labeled data in the target domain $\cD_T$, foreseeing performance gain on the target task $\cX_T$ will improve, after initial training on $\cX_S$ and additional training on $\cX_T$. Zero-shot learning thus refers to immediate test on $\cX_T$ after initial training on $\cX_S$.
